\input{header.tex}

\topbit{Thoughts about gravitational wave follow-up and LIGO triggering}{15 June 2017}
       {GW, LIGO}

\section{Signals}

\frame{\frametitle{Might gravitational wave events be coincident
  with cosmic ray or neutrino transients?}

\ul

\item Black hole/black hole mergers

\ul

  \item I'm not aware of a plausible mechanism

  \item All LIGO events so far

\lu

\item Neutron star/neutron star mergers

\ul

  \item Clearly are going to make some neutrinos.  Any predictions for the flux

\lu

\item Neutron star/black hole mergers

\ul

\item Probably not?

\lu

\item Supernovae

\ul

  \item  Obviously

\lu

\lu

}

\section{NOvA work so far}

\frame{\frametitle{So far}

\ul

\item Alec took a look our data coincident with the first
LIGO event in \href{http://nova-docdb.fnal.gov:8080/cgi-bin/ShowDocument?docid=14351}{doc-14351}

\item Was on 2015-09-14, during shutdown.  Data was ``ratty'', in Alec's words.

  \ul

    \item I think only FD was looked at?

    \item ND was running smoothly.

  \lu


\item 2nd good LIGO event on 2015-12-26 3:38:53:

  \ul
  \item Both detectors running smoothly.
  \lu

\item 3rd good LIGO event on 2017-01-04 10:11:58.6 UTC

  \ul
  \item Both detectors running smoothly.
  \lu

\item Marginal LIGO event on 2016-10-12 9:54:43 UTC

  \ul
  \item FD down ``Error in DataLogger''. 
  \item ND ok.
  \lu

\lu

}

\section{Analysis}

\frame{\frametitle{Analysis}

Signals:

\ul

\item Low-to-medium energy cosmics: FD samples lower energy muons, ND higher energy

\item High-energy cosmics: Look for large showers

\item MeV neutrinos: supernova-like signal (or just \emph{supernova} signal)

\item GeV neutrinos: upward-going muons or burst of contained events in any direction

\lu

Do we have unique capabilities?

\ul

\item Lower energy muons?  Maybe.

\item Higher energy muons? Seems less likely.  Cosmic ray arrays are better
suited to this.

\item For MeV neutrinos, yes.  We are a large carbon detector and provide 
flavor information when combined with detectors of other compositions.

\item GeV neutrons: Probably.  Our mass is comparable to Super-K.

\lu

}

\section{Triggering}

\frame{\frametitle{}

\ul

\item Our only data for the LIGO events so far is sampled at 0.55\% by the 10\,Hz 
trigger, plus O(0.1\%) by other triggers

\item Would be lovely to have all the data instead

\lu

}

\beginbackup

\frame{\frametitle{Backups}}

\backupend
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
